---
title: "languageR Instructions"
author: "Zhang Le, Data Scientist, Microsoft"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Introduction

Text analysis becomes an essential part in contemporary advanced analytics and artificial intelligence applications. Building complete text analytics framework/system in R takes considerable work and time. `languageR` provides out-of-box methods for text analytics such as translation, sentiment analysis, topic detection, etc, with the help of Microsoft Cognitive Service APIs, which simplify the process of text analysis in R environment. 

### Preliminaries

The `languageR` functions call APIs of Microsoft Cognitive Services. Subscription of Microsoft Azure is therefore required to obtain the key corresponding to a service. 

Generally, before using the `languageR` functions, one needs to 

1. Apply an Azure account. Free trial is available.
2. Deploy Cognitive Service in the market place at [Azure Portal](https://portal.azure.com/). In the deployment, select the specific service (e.g., Text Analytics) to be hosted on the cloud. 
3. Get the API Key of the deployed cognitive service.
4. Use `languageR::apiInfo()` or `languageR::apiInfo("function name")` to list information of all APIs or a specific one.

More details can be found at the [website](https://www.microsoft.com/cognitive-services/en-us/apis).

### Text analytics functions

#### Translation
`cognitiveTranslation` translates input text from source language to target language. It also accounts for convention differences for the same language but different locales. For example, **big data** is translated into **大数据** for Simplified Chinese but **大資料** for Traditional Chinese.
```{r, eval=FALSE, echo=TRUE}
text <- "大数据"

translated_text1 <- cognitiveTranslation(text, lanFrom="zh-CHS", lanTo="en", apiKey="a valid key")
translated_text1
# [1] "Big data"

text <- "Big Data"
translated_text2 <- cognitiveTranslation(text, lanFrom="en", lanTo="zh-CHS", apiKey="a valid key")
translated_text2
# [1] "大数据"

translated_text3 <- cognitiveTranslation(text, lanFrom="en", lanTo="zh-CHT", apiKey="a valid key")
translated_text3
# [1] "大資料"
```

#### Sentiment analysis
`cognitiveSentiAnalysis` produces sentiment score, ranging from 0 (negative) to 1 (positive), for the given text. 
```{r, eval=FALSE, echo=TRUE}
senti_score <- cognitiveSentiAnalysis("I love you", apiKey="a valid key string")
senti_score
# $documents
#       score id
# 1 0.9140102  1
# 
# $errors
# list()

text <- c("I love you", "I hate you", "This is love")
senti_scores <- cognitiveSentiAnalysis(text, apiKey="a valid key string")
senti_scores
# $documents
#        score id
# 1 0.91401020  1
# 2 0.05904578  2
# 3 0.91798760  3
# 
# $errors
# list()
```

#### Language detection
`cognitiveLangDetect` detects the language of input text. Number of languages for detection can be specified (default is 1).
```{r, eval=FALSE, echo=TRUE}
lang1 <- cognitiveLangDetect("English", apiKey="a valid key string")
lang1
# $documents
#   id detectedLanguages
# 1  1    English, en, 1
# 
# $errors
# list()

langs2 <- cognitiveLangDetect(c("English", "大数据"), langNum=2, apiKey="a valid key string")
langs2
# $documents
#   id             detectedLanguages
# 1  1                English, en, 1
# 2  2 Chinese_Simplified, zh_chs, 1
# 
# $errors
# list()
```

#### Topic detection
`cognitiveTopicDetect` extracts topics of given text documents. Note the minimum number of documents for topic detection is 100. The function returns error if document size is smaller. BBC news articles of 5 topics, each of which contains 50 articles, are attached for experiments.
```{r, eval=FALSE, echo=TRUE}
data(text_bbc)

topics_detected <- cognitiveTopicDetect(text_bbc, apiKey="a valid key")
topics_detected
```

#### Key phrase detection
`cognitiveKeyPhrases` extracts key phrases from given text.
```{r, eval=FALSE, echo=TRUE}
key_phrases <- cognitiveKeyPhrases("Artificial Intelligence is regarded as one of the disruptive technologies in the 21st century", apiKey="a valid key string")
key_phrases
# $documents
#                                                  keyPhrases id
# 1 disruptive technologies, century, Artificial Intelligence  1
# 
# $errors
# list()
```

#### Spelling check
`cognitiveSpellingCheck` checks spelling of given text and return the detected wrongly spelt words (associated with confidence as probability) as well as suggested ones for replacement.
```{r, eval=FALSE, echo=TRUE}
text <- c("today is holliday", "hapyp new yaer")

text_detected <- cognitiveSpellingCheck(text, apiKey="a valid key")
text_detected
# $`_type`
# [1] "SpellCheck"
# 
# $flaggedTokens
#   offset    token         type                suggestions
# 1      9 holliday UnknownToken holiday, 0.884147790762446
# 2     18    hapyp UnknownToken   happy, 0.884147790762446
# 3     28     yaer UnknownToken    year, 0.884147790762446
```

#### Linguistic Analytics
`cognitiveLinguiAnalysis` returns tokenized results with offset and part-of-speech information of given text. 
```{r, eval=FALSE, echo=TRUE}
text <- "What did you say?!? I didn't hear about the director's new proposal. It's important to Mr. and Mrs. Smith"

tokens <- cognitiveLinguiAnalysis(text, apiKey="a valid key")
tokens
#                             analyzerId
# 1 22a6b758-420f-4745-8a3c-46835a67c0d2
# 2 4fa79af1-f22c-408d-98bb-b7d7aeef7f04
# 3 08ea174b-bfdb-4e64-987e-602f85da7f72
#                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            result
# 1                                                                                                           (TOP (SBARQ (WHNP (WP What)) (SQ (VBD did) (NP (PRP you)) (VP (VB say)) (. ?)) (. !) (. ?))), (TOP (S (NP (PRP I)) (VP (VBD did) (RB n't) (VP (VB hear) (PP (IN about) (NP (NP (DT the) (NN director) (POS 's)) (JJ new) (NN proposal))))) (. .))), (TOP (S (NP (PRP It)) (VP (VBZ 's) (ADJP (JJ important) (PP (TO to) (NP (NP (NNP Mr.)) (CC and) (NP (NNP Mrs.) (NNP Smith))))))))
# 2                                                                                                                                                                                                                                                                                                                                                                                   WP, VBD, PRP, VBP, ., ., ., PRP, VBD, RB, VB, IN, DT, NN, POS, JJ, NN, ., PRP, VBZ, JJ, TO, NNP, CC, NNP, NNP
# 3 19, 48, 36, 0, 20, 69, 4, 3, 3, 3, 1, 1, 1, What, did, you, say, ?, !, ?, 0, 5, 9, 13, 16, 17, 18, What, did, you, say, ?, !, ?, 1, 3, 3, 4, 5, 3, 8, 2, 3, 8, 1, I, did, n't, hear, about, the, director, 's, new, proposal, ., 20, 22, 25, 29, 34, 40, 44, 52, 55, 59, 67, I, did, n't, hear, about, the, director, 's, new, proposal, ., 2, 2, 9, 2, 3, 3, 4, 5, It, 's, important, to, Mr., and, Mrs., Smith, 69, 71, 74, 84, 87, 91, 95, 100, It, 's, important, to, Mr., and, Mrs., Smith
```