---
title: "cognitiveR Instructions"
author: "Zhang Le, Data Scientist, Microsoft"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Introduction

Use `cognitiveR` for text analytics such as translation, sentiment analysis, topic detection, etc.

### Preliminaries

All of the functionsin `cognitiveR` call APIs of Microsoft Cognitive Services. Subscription of Microsoft Azure is therefore required to obtain the key corresponding to a service. More details can be found at the [website](https://www.microsoft.com/cognitive-services/en-us/apis).

### Text analytics

Text analytics are intensively applied in many application scenarios. To name a few, document classification, sentiment analysis of social media posts, and topic detection in news articles. 

#### Translation
`cognitiveTranslation` translates text in source language to target language. It also accounts for convention differences for the same language but different locales. For example, **big data** is translated into **大数据** for Simplified Chinese but **大資料** for Traditional Chinese.
```{r, eval=FALSE, include=FALSE}
text <- "人工智能"

translated_text1 <- cognitiveTranslation(text, lanTo="en", apiKey="a valid key")
translated_text1

text <- "人工智能 big data"
translated_text2 <- cognitiveTranslation(text, lanFrom="en", lanTo="zh-CHS", apiKey="a valid key")
translated_text2

translated_text3 <- cognitiveTranslation(text, lanFrom="en", lanTo="zh-CHT", apiKey="a valid key")
translated_text3
```

#### Sentiment analysis
`cognitiveSentiAnalysis` produces sentiment score, ranging from 0 (negative) to 1 (positive), for the given text.
```{r, eval=FALSE, include=FALSE}
senti_score <- cognitiveSentiAnalysis("I love you", apiKey="a valid key string")
senti_score

text <- c("I love you", "I hate you", "This is love")
senti_scores <- cognitiveSentiAnalysis(text, apiKey="a valid key string")
senti_scores
```

#### Language detection
`cognitiveLangDetect` detects the language of input text. Number of languages for detection can be specified (default is 1).
```{r, eval=FALSE, include=FALSE}
lang1 <- cognitiveLangDetect("English", apiKey="a valid key string")
lang1

langs2 <- cognitiveLangDetect(c("English", "中文"), langNum=2, apiKey="a valid key string")
langs2
```

#### Topic detection
`cognitiveTopicDetect` extracts topics of given text documents. Note the minimum number of documents for topic detection is 100. The function returns error if document size is smaller. BBC news articles of 5 topics, each of which contains 50 articles, are attached for experiments.
```{r, eval=FALSE, include=FALSE}
data(text_bbc)

topics_detected <- cognitiveTopicDetect(text_bbc, apiKey="a valid key")
topics_detected
```

#### Key phrase detection
`cognitiveKeyPhrases` extracts key phrases from given text.
```{r, eval=FALSE, include=FALSE}
key_phrases <- cognitiveKeyPhrases("Artificial Intelligence is regarded as one of the disruptive technologies in the 21st century", apiKey="a valid key string")
key_phrases
```

#### Spelling check
`cognitiveSpellingCheck` checks spelling of given text and return the detected wrongly spelt words (associated with confidence as probability) as well as suggested ones for replacement.
```{r, eval=FALSE, include=FALSE}
text <- c("today is holliday", "hapyp new yaer")

text_detected <- cognitiveSpellingCheck(text, apiKey="a valid key")
text_detected
```

#### Linguistic Analytics
`cognitiveLinguiAnalysis` returns tokenized results with offset and part-of-speech information of given text. 
```{r, eval=FALSE, include=FALSE}
text <- "What did you say?!? I didn't hear about the director's new proposal. It's important to Mr. and Mrs. Smith"

tokens <- cognitiveLinguiAnalysis(text, apiKey="a valid key")
tokens
```